Nowadays, every single industry uses the inventory management system to manage its inventory. The most leading company that has adopted this feature in the system are dear systems, Cin7, unleashed, etc who have been charging fees between £149 - £200. By involving a higher fee the small business cannot afford to pay for their service. Therefore, I am building a system to help a small business like a corner shop with no extra costs.

\section{Motivation \& Aims}
The aim of this project is to help small business specially corner shop to manage their inventory. From my personal experience, while working in my uncle's shop who uses a spreadsheet to manage his entire inventory, and sometimes he does not even know if he has run the item or not. He always goes around the shop to check which item has been out of stock and manually enter in a piece of paper to get them from cash \& carry(Wholesaler) or supplier. The current system they are using not time efficient therefore I want to help my uncle and other local shops like him to use my system to save time and money. This system will require an internet connection to get the data from the database and shows on user browser.\newline
\newline This concept has various applications to other scenarios such as using a bar code to find a piece of item information using a scanner. It could also use machine learning to identify product availability in the inventory using the camera. Inventory check was created using HTML, CSS, JavaScript, PHP, MySQL, and API.

\section{Purpose \& Scope}
The purpose of this project is to give a solution to a local shop to manage their inventory stock. The important part of this project is achieved by adding a product, edit product, delete a product, view all products, use the search bar to find the specific item, and analyse the data which will be displayed in bar chart/table.

\section{Section Overview}
This report will contain six main sections:
\begin{enumerate}
    \item \textbf{Introduction}: This section will outline the motivation, aims, purpose, and scope of the project.
    
    \item \textbf{Background Research}: Analysing the existing system, technical research to find useful technology to use in this project, public survey, Software architecture, and back-end software.
    
    \item \textbf{System Design}: This section consists of system requirements, use case diagram, wireframe(UI), side map, and accessibility features of the application.
    
    \item \textbf{Implementation}: Discussion of implementation with Front-end development, PHP, MySQL, Telegram API, and Gantt chart. This shows how this technology helps me build this system.
    
    \item \textbf{Testing}: A formal testing was done to see how the system was performing. This was done with Normal testing, User testing, and deployment.
    
    \item \textbf{Conclusion}: This session evaluates the success of the implementation which was discovered in background research. It analyses the system successes, system failure, and future development that could be happening in future development.

    
\end{enumerate}

In addition, this report contains a number of different appendices:
\begin{enumerate}
    \item \textbf{Appendix A} - Full list of responses that was gathered throughout the public questionnaire.
    \item \textbf{Appendix B} - This will show you where you find the inventory check code file from GitLab.
    \item \textbf{Appendix C} - A list of instructions to run the server and application to view the website.
\end{enumerate}
