After development different testing was conducted to improve the system and limit the bugs. When features were implemented, I have reviewed the code that ensures any defective areas in the code and also improves the quality of the code such as adding comments, better code layout, etc. I have implemented two different types of testing such as normal testing (Tested by myself) and user testing ( Tested by my friend). User testing was supposed to be done by my uncle but due to the Covid-19 virus, I could not able to go outside my house and my uncle does not know how to install the required software to run the program. Therefore I have decided to give my program to one of my friend JayKumar who has tested my program using a conference call on the Zoom app.

\section{Normal Testing}

\begin{longtable}{| p{4em} | p{9em}| p{9em} |  p{9em} |  p{4em} | } \\

\hline 
\multicolumn{1}{|c|}{\textbf{Test No}} & \multicolumn{1}{c|}{\textbf{Description}} & \multicolumn{1}{c|}{\textbf{Expected Result}} & \multicolumn{1}{c|}{\textbf{Actual Result}} & \multicolumn{1}{c|}{\textbf{Pass/Fail}}\\ \hline
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- Continued From Previous Page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Test No}} & \multicolumn{1}{c|}{\textbf{Description}} & \multicolumn{1}{c|}{\textbf{Expected Result}} & \multicolumn{1}{c|}{\textbf{Actual Result}} & \multicolumn{1}{c|}{\textbf{Pass/Fail}}\\ \hline
\endhead

\multicolumn{3}{|r|}{{Continued on next page}} \hline
\endfoot

\hline 

\hline
\endlastfoot

1 & Check all the navigation link & Should take to right page & Has taken to correct page & Pass \\ 
\hline
2 & User should able to login  & Should able to redirect to product page & Does not take anywhere & Fail \\

\hline
3 & User should able to create a new account  & Should able to redirect to login page & Does not take anywhere & Fail \\

\hline
4 & User clicked on View all product button from product page  & Should able to redirect to view all product page & It has taken to view all product page & Pass \\

\hline
5 & User clicked on add product button from product page  & Should able to redirect to add product page where user can add product & It has taken to add product page where user can add product & Pass \\

\hline
6 & User use the search functionality to search for specific product  & Should able to show relevant product based on user search & It shows all the relevant product & Pass \\

\hline
7 & User should able to edit the product using edit button from view all product page  & Should able to take the user to edit form & It has taken the user to edit form where they can edit the data & Pass \\

\hline
8 & User should able to delete the product using delete button from view all product page  & Should able to delete entire record from the database & It has deleted the entire record from the database & Pass \\

\hline
9 & User should able to see correct remaining quantity value & Should able to change the value automatically & It has changed the remaining quality automatic & Pass \\

\hline
10 & Database need to display all the product in the view all product page  & User should able to see all the product & User can see all the product & Pass \\

\hline
11 & User should able to add product in the database from add product page  & Ability to add the product in the database & It has successfully added the product & Pass \\

\hline
12 & User should able to see an error message if there is no record in the database & Display the message & The message shown when there is no records & Pass \\

\hline
13 & Error message if the user forgot to fill the field when adding product & Display alert ("Please fill in this field") & Shows the alert in user screen & Pass \\

\hline
14 & User should able to view the chart from analytic page & Display the correct chart & shows the right chart & Pass \\

\hline
15 & User should able to send a message using contact form & Message should be sent successfully  & It has sent the message successfully & Pass \\

\hline
16 & User should able to logout from the system  & Take back the user to login page & Does not take anywhere & Fail \\

\end{longtable}

\section{User Testing}
It is used to help me to get a better understanding of the system from my friend. The feedback that was received by my friend will help me to improve the system performance, design in future development. This could be added before deploying the system in the market. I have asked one of my friends to test the program and give useful feedback through an online conference in Zoom. I have asked a number of different question related to user experience and features of the program.\newline 
\newline The following lists are the question and his reply while testing the program.

\begin{enumerate}
    \item \textbf{How easy was it to navigate around the website?} \\
    It was very easy to navigate around the side as you have kept the site simple and easy to use. 
    
    \item \textbf{Does all the navigation links takes you to the right page?}\\
    It does take me to the right page when I click on the links but the logout button does not do anything. This feature will be added in future development.
    
    \item \textbf{ Were you able to view all product?}\\
    Yes, I can see all the items in the view of all product pages that I have stored in the database using add product form.
    
    \item \textbf{ Were you able to add the product in the database?}\\
    Yes, I was able to add the product using the form in the add product page and I can see the newly added product in view all product page at the beginning of all the items.
    
    \item \textbf{ Were you able to edit the product?}\\
    Yes, when I clicked on edit button it took me to edit form where I have edited and update the product.
    
    \item \textbf{ Were you able to delete the product?}\\
    Yes, I was able to delete the product but it could be useful to add a confirmation dialog box. This feature will come in future development.
    
    \item \textbf{ Were you able to search a product using search box?}\\
    Yes, I was able to see all the relevant product when I type the word "A". It shows me all the products that contain the letter "A". I have even tried to search a product using item numbers to find the specific product and in return, it shows me the correct data.
    
    \item\textbf{How useful was the chart?}\\
    It was very useful to see the number of sold items in a bar chart format and also to see the total cost from the wholesale price, in-store price, profit between wholesale product/in-store, and total sale on a sold item. This was the best feature that you have added to your website.
    
    \item\textbf{How easy to contact the developer?}\\
    It was very easy to contact the developer using the contact form and once I submit the form it gave me a useful message as "Thankyou for your message!"
    
    \item \textbf{Do you consider the app to be helpful?}\\
    Yes of course as it will help all the shop keeper to manage their inventory who are using spreadsheets until now.
    
    \item \textbf{Will you recommend this website to your friend and family who own business?} \\
    Yes, this was the best app I have ever seen for the local shopkeeper.  
    
    \item \textbf{Is there anything else I should know about the system? }\\
    Yes, Your login, logout, and create new account functionality is not working. I know and this feature will be added in a later version of the website.
\end{enumerate}

\section{Deployment}
Once the application is ready and successfully released on the server, an email will be sent to my clients. This will ensure that the system is successful reaches the users and the required features are delivered successfully. The following list is a procedure for deploying the system:
\begin{enumerate}
    \item Make sure everything is done which includes adding all the important features.
    \item Making sure all the functions are working properly.
    \item Email the clients for a meeting where I will present the application.
    \item If everything goes well then sign off documents to use the system free of charge.
\end{enumerate}